---
title: "Policing sentiment in Montreal, 2015-2020"
output: html_document
---

```{r, include = FALSE}
library(tidyverse)
library(ggplot2)
library(ggrepel)
library(sf)

load("media.Rdata")
load("ner.Rdata")
load("ner_locations.Rdata")
load("boroughs.Rdata")
load("censusbyborough.Rdata")

ner_locations <-
  ner_locations %>% 
  st_as_sf() %>% 
  st_join(boroughs) %>% 
  filter(!is.na(borough))
```


## Overall policing sentiment per borough

```{r, echo = FALSE, message = FALSE, error = FALSE}
media %>% 
  inner_join(ner_locations) %>% 
  add_count(borough) %>%   
  filter(n > 100) %>%      
  group_by(borough) %>% 
  summarise(sentiment_mean = mean(sentiment, na.rm = TRUE)) %>% 
  inner_join(boroughs) %>% 
  st_as_sf() %>%
  ggplot() +
  geom_sf(aes(fill = sentiment_mean)) +
  geom_sf(data = boroughs, colour = "black", fill = NA) +
  labs(title = "policing sentiment per borough",
       fill = "sentiment")+
  theme_minimal()
```


## Policing sentiment related to "racism"

```{r, echo = FALSE, message = FALSE, error = FALSE}
media %>% 
  filter(str_detect(text, "racism")) %>% 
  inner_join(ner_locations) %>% 
  group_by(borough) %>% 
  summarise(sentiment_mean = mean(sentiment, na.rm = TRUE)) %>% 
  inner_join(boroughs) %>% 
  st_as_sf() %>%
  ggplot() +
  geom_sf(aes(fill = sentiment_mean)) +
  geom_sf(data = boroughs, colour = "black", fill = NA) +
  labs(title = "policing sentiment per borough",
       fill = "sentiment")+
  theme_minimal()
```


## Policing sentiment related to "discrimination"

```{r, echo = FALSE, message = FALSE, error = FALSE}
media %>% 
  filter(str_detect(text, "discrimination")) %>% 
  inner_join(ner_locations) %>% 
  group_by(borough) %>% 
  summarise(sentiment_mean = mean(sentiment, na.rm = TRUE)) %>% 
  inner_join(boroughs) %>% 
  st_as_sf() %>%
  ggplot() +
  geom_sf(aes(fill = sentiment_mean)) +
  geom_sf(data = boroughs, colour = "black", fill = NA) +
  labs(title = "policing sentiment per borough",
       fill = "sentiment")+
  theme_minimal()
```


## Policing sentiment related to "systemic"

```{r, echo = FALSE, message = FALSE, error = FALSE}
media %>% 
  filter(str_detect(text, "systemic")) %>% 
  inner_join(ner_locations) %>% 
  group_by(borough) %>% 
  summarise(sentiment_mean = mean(sentiment, na.rm = TRUE)) %>% 
  inner_join(boroughs) %>% 
  st_as_sf() %>%
  ggplot() +
  geom_sf(aes(fill = sentiment_mean)) +
  geom_sf(data = boroughs, colour = "black", fill = NA) +
  labs(title = "policing sentiment per borough",
       fill = "sentiment")+
  theme_minimal()
```


##  Relationship between policing sentiment and Black population

```{r, echo = FALSE, message = FALSE, error = FALSE}
media %>% 
  inner_join(ner_locations) %>% 
  add_count(borough) %>%   # counts the number of matches per borough
  filter(n > 100) %>%      # filters out the boroughs with less than 100 matches, for calculation
  group_by(borough) %>% 
  summarise(average_sentiment = mean(sentiment, na.rm = TRUE)) %>% 
  right_join(censusbyborough) %>% 
  filter(!is.na(average_sentiment)) %>%    # filters out the boroughs with less than 100 matches, for plotting
  st_as_sf() %>% 
  ggplot(aes(x = average_sentiment, y = black_pct_pop, colour = borough)) +
  geom_point(alpha = 0.5, size = 5) +
  geom_label_repel(aes(label = borough), size = 3, box.padding = 0.25, point.padding	= 0.5, segment.color = "grey50") +
  scale_x_continuous(name = "Mean Sentiment Score") +
  scale_y_continuous(name = "Black Population (%)") +
  labs(title = "Relationship between policing sentiment and Black population",
       subtitle = "Montreal, per borough") +
  theme_minimal() +
  theme(legend.position = "none")
```


##  Relationship between policing sentiment and indigenous population

```{r, echo = FALSE, message = FALSE, error = FALSE}
media %>% 
  inner_join(ner_locations) %>% 
  add_count(borough) %>%   # counts the number of matches per borough
  filter(n > 100) %>%      # filters out the boroughs with less than 100 matches, for calculation
  group_by(borough) %>% 
  summarise(average_sentiment = mean(sentiment, na.rm = TRUE)) %>% 
  right_join(censusbyborough) %>% 
  filter(!is.na(average_sentiment)) %>%    # filters out the boroughs with less than 100 matches, for plotting
  st_as_sf() %>% 
  ggplot(aes(x = average_sentiment, y = indigenous_pct_pop, colour = borough)) +
  geom_point(alpha = 0.5, size = 5) +
  geom_label_repel(aes(label = borough), size = 3, box.padding = 0.25, point.padding	= 0.5, segment.color = "grey50") +
  scale_x_continuous(name = "Mean Sentiment Score") +
  scale_y_continuous(name = "Low-income Population (%)") +
  labs(title = "Relationship between policing sentiment and indigenous population",
       subtitle = "Montreal, per borough") +
  theme_minimal() +
  theme(legend.position = "none")
```


##  Relationship between policing sentiment and low-income population

```{r, echo = FALSE, message = FALSE, error = FALSE}
media %>% 
  inner_join(ner_locations) %>% 
  add_count(borough) %>%   # counts the number of matches per borough
  filter(n > 100) %>%      # filters out the boroughs with less than 100 matches, for calculation
  group_by(borough) %>% 
  summarise(average_sentiment = mean(sentiment, na.rm = TRUE)) %>% 
  right_join(censusbyborough) %>% 
  filter(!is.na(average_sentiment)) %>%    # filters out the boroughs with less than 100 matches, for plotting
  st_as_sf() %>% 
  ggplot(aes(x = average_sentiment, y = total_LICO_pct_pop, colour = borough)) +
  geom_point(alpha = 0.5, size = 5) +
  geom_label_repel(aes(label = borough), size = 3, box.padding = 0.25, point.padding	= 0.5, segment.color = "grey50") +
  scale_x_continuous(name = "Mean Sentiment Score") +
  scale_y_continuous(name = "Low-income Population (%)") +
  labs(title = "Relationship between policing sentiment and low-income population",
       subtitle = "Montreal, per borough") +
  theme_minimal() +
  theme(legend.position = "none")
```


##  Relationship between policing sentiment and immigrant population

```{r, echo = FALSE, message = FALSE, error = FALSE}
media %>% 
  inner_join(ner_locations) %>% 
  add_count(borough) %>%   # counts the number of matches per borough
  filter(n > 100) %>%      # filters out the boroughs with less than 100 matches, for calculation
  group_by(borough) %>% 
  summarise(average_sentiment = mean(sentiment, na.rm = TRUE)) %>% 
  right_join(censusbyborough) %>% 
  filter(!is.na(average_sentiment)) %>%    # filters out the boroughs with less than 100 matches, for plotting
  st_as_sf() %>% 
  ggplot(aes(x = average_sentiment, y = immigrant_pct_pop, colour = borough)) +
  geom_point(alpha = 0.5, size = 5) +
  geom_label_repel(aes(label = borough), size = 3, box.padding = 0.25, point.padding	= 0.5, segment.color = "grey50") +
  scale_x_continuous(name = "Mean Sentiment Score") +
  scale_y_continuous(name = "Low-income Population (%)") +
  labs(title = "Relationship between policing sentiment and immigrant population",
       subtitle = "Montreal, per borough") +
  theme_minimal() +
  theme(legend.position = "none")
```


##  Relationship between policing sentiment and refugee population

```{r, echo = FALSE, message = FALSE, error = FALSE}
media %>% 
  inner_join(ner_locations) %>% 
  add_count(borough) %>%   # counts the number of matches per borough
  filter(n > 100) %>%      # filters out the boroughs with less than 100 matches, for calculation
  group_by(borough) %>% 
  summarise(average_sentiment = mean(sentiment, na.rm = TRUE)) %>% 
  right_join(censusbyborough) %>% 
  filter(!is.na(average_sentiment)) %>%    # filters out the boroughs with less than 100 matches, for plotting
  st_as_sf() %>% 
  ggplot(aes(x = average_sentiment, y = refugee_pct_pop, colour = borough)) +
  geom_point(alpha = 0.5, size = 5) +
  geom_label_repel(aes(label = borough), size = 3, box.padding = 0.25, point.padding	= 0.5, segment.color = "grey50") +
  scale_x_continuous(name = "Mean Sentiment Score") +
  scale_y_continuous(name = "Low-income Population (%)") +
  labs(title = "Relationship between policing sentiment and refugee population",
       subtitle = "Montreal, per borough") +
  theme_minimal() +
  theme(legend.position = "none")
```


## Average policing sentiment from 2015-01-01 to 2020-06-30

```{r, echo = FALSE, message = FALSE, error = FALSE}
media %>% 
#  filter(str_detect(text, "systemic")) %>% 
  filter(date >= "2015-01-01", date <= "2020-06-30") %>%
  group_by(date) %>%
  summarize(avg_sentiment = mean(sentiment)) %>%
  ggplot(aes(date, avg_sentiment)) +
  geom_line() +
  geom_smooth()+
  theme_minimal()
```


## Average policing sentiment from 2020-01-01 to 2020-06-30

```{r, echo = FALSE, message = FALSE, error = FALSE}
media %>% 
#  filter(str_detect(text, "systemic")) %>% 
  filter(date >= "2015-01-01", date <= "2020-06-30") %>%
  group_by(date) %>%
  summarize(avg_sentiment = mean(sentiment)) %>%
  ggplot(aes(date, avg_sentiment)) +
  geom_line() +
  geom_smooth()+
  theme_minimal()+
  tidyquant::coord_x_date(xlim = c("2020-01-01", "2020-06-30"),
               ylim = c(-0.15, 0.025))+
  geom_vline(xintercept = as.numeric(as.Date('2020-05-25')), colour = "red")
```


